Enhancement of SDR in Thessaloniki

### 2024-09-10 GHI_enh_04_investigate.tex
Commit 2024-09-07 19:12
Commit 2024-09-08 12:14
Commit 2024-09-08 20:14
Commit 2024-09-08 21:12
Commit 2024-09-08 22:14
Commit 2024-09-10 10:15
Commit 2024-09-10 11:09

@@

\begin{verbatim}
Attaching package: 'ggpubr'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:cowplot':

    get_legend
\end{verbatim}

\begin{verbatim}
The following objects are masked from 'package:ggpp':

    as_npc, as_npcx, as_npcy
\end{verbatim}

@@

@@

\begin{verbatim}
2024-09-06 10:26:49.9 athan@sagan GHI_enh_04_investigate.R 10.084896 mins
\end{verbatim}

>>>>

{[}1{]} 0
Duration \textless{} 5 minutes 73.5 \%

Duration \textless=5 minutes 79.3 \%

Duration \textgreater{} 10 minutes 7.7 \%

{[}1{]} 8

@@

@@

TableGrob (2 x 3) ``arrange'': 4 grobs
z cells name grob
1 1 (1-1,2-2) arrange gtable{[}layout{]}
2 2 (1-1,3-3) arrange gtable{[}layout{]}
3 3 (2-2,2-3) arrange text{[}GRID.text.696{]}
4 4 (1-2,1-1) arrange text{[}GRID.text.694{]}
TableGrob (2 x 3) ``arrange'': 4 grobs
z cells name grob
1 1 (1-1,2-2) arrange gtable{[}layout{]}
2 2 (1-1,3-3) arrange gtable{[}layout{]}
3 3 (2-2,2-3) arrange text{[}GRID.text.696{]}
4 4 (1-2,1-1) arrange text{[}GRID.text.694{]}

@@

\begin{verbatim}
2024-09-10 07:46:40.3 athan@sagan GHI_enh_04_investigate.R 1.579120 mins
\end{verbatim}
